---
title: "A6 Who Represents You?"
author: "Ryan Leung"
date: "May 13, 2019"
output: html_document
---

```{r, warning=FALSE, message=FALSE, echo=FALSE}
# Sets address and source files
source("api-keys.R")
source("civic-info.R")
source("propublica.R")
```
#Introduction
This report provides information on current **Oregon state** representatives, it also describes the  
gender ratio of current Oregon politicians as well as the ratio between **Democratic** vs   **Republican**. For this report I used my home address back in Oregon. My address is `r my_address`.  
The following are the **api** links:  
- [Google Civics Info](`r civic_uri`)  
- [Propublica](`r end_point_pub`)

#Table of Political Representatives
```{r table, echo = FALSE}
kable(or_rep_v5, col.names = c("Name", "Position", "Party", "Email", "Phone", "Photo"))
```

#Representatives by **Gender** in Oregon
```{r gender plot, echo = FALSE}
gender_plot
```

#Representatives by **Party** in Oregon
```{r party plot, echo = FALSE}
party_plot
```

#**Suzanne Bonamici**, Oregon Representative
Suzanne Bonamici is a representative for Oregon. She is **`r rep_age`** years old, and her _Twitter_ is  
[`r username`](`r twitter`). Suzanne agrees with **`r vote_percent`%** of votes.